\begin{abstractEN}

    Heart disease has overtaken all other causes of death in the population in recent years due to an increase in prevalence.
    A crucial tool for the early diagnosis of cardiovascular disorders is ambulatory electrocardiogram (ECG) monitoring.
    The demand for mobile ECG monitoring applications is increasing significantly as a result of the acceptance of smaller wearable Holter monitoring devices and the proliferation of mobile devices.
    On the other hand, the abundance of ambulatory ECG data has increased the need for automatic ECG analysis algorithms, and numerous artificial intelligence ambulatory ECG analysis algorithms have evolved as a result of the quick development of deep learning models.

    Based on the existing dynamic ECG artificial intelligence analysis algorithms and mobile application development technologies, this project designed and implemented a wearable dynamic ECG intelligent monitoring application for mobile terminals.
    The context and relevance of the project are first discussed, followed by an analysis of relevant technologies and a choice of technologies.
    The requirement analysis of the application is then finished, and the requirements for ECG, analysis reports, and device management are determined.
    Then, the application's modules were split up using Flutter's Riverpod architecture pattern.
    The existing model was ported with the LibTorch framework during the development phase, and then cross-platform development using the Flutter framework was done to make the application compatible with the two most popular mobile operating systems, Android and iOS. Last but not least, testing of the program was done to ensure that it is comprehensive and functional, with a user-friendly interface for patients.


\end{abstractEN}
